% html: Beginning of file: `experience.html'
\begin{description}
\item[] \begin{description}
\item[] {\large \bf Experience}\newline
\newline
{\bf 1976-1977:}
Pietermaritzburg,\newline
Assistant Train Driver. \newline
\newline
{\bf 1977-1978:}
Natal Provincial Administration in Pietermaritzburg, \newline
Scientific Programmer. \newline
 \newline
{\bf 1979-1984:}
Rhodes University, Computing Services, \newline
Scientific Programmer.  
\begin{itemize}
\item Last position held: Head of Academic Support,
           responsible for user training, package installation/maintenance
           and various development projects.
%\item Software: Fortran, Pascal, Cobol, Lisp, MuSimp, SPSS, IMSL,
%           Graphics, Databases, Debtors, Electronic mail,
%           Micro/Mainframe communications, Word processing and Spreadsheets.
%\item Hardware: ICL 1904S under MAXIMOP and GEORGE2, CDC CYBER825
%           under NOS, APPLE-II under CP/M, IBM PC under DOS, Windows and Unix.
\end{itemize}

{\bf 1985-1986:}
Department of Mathematics, Rhodes University, \newline
Lecturer. \newline
\newline
{\bf 1987-2003:}
Department of Computer Science, Natal University, \newline
Senior Lecturer and Associate Professor (Durban campus). \newline
\newline
{\bf 2004-2014:}
School of Computer Science, University of KwaZulu-Natal,  \newline
Professor (Pietermaritzburg campus)
\begin{itemize}
\item  Head of School (Pietermaritzburg and Durban) (2005-2007)
\item  PI for Bioinformatics grant (2006-2009)
\item  Deputy Head  of School (2009-2010)
\item  Head  of School (2011)
\end{itemize}

{\bf 2015-\ldots}
Contracting:

\begin{itemize}
\item contract teaching: Computer Science, UKZN.
\item consulting.
\end{itemize}


\newpage
\item[] {\large \bf Teaching}\newline
\newline
{\large \bf Mathematics courses taught (1985-1986)}

 \begin{itemize} 
  \item[] Calculus, Numerical Analysis, Linear Algebra, \newline
       Differential Equations, Complex Variables.
 \end{itemize}

{\large \bf  Computer Science courses taught (1987-2014)}
\begin{itemize}
\item[]  Discrete Maths, Introduction to Programming, Computer Literacy, \newline
             Object Oriented Programming, Data Structures, \newline
             Operating Systems, Graphics, \newline
             Image Processing, Mathematical Modeling, \newline
             Bioinformatics, Data Mining
\end{itemize}


{\large \bf Contract teaching (2015 - 2018)}
\begin{itemize}
	\item[] honours: Bioinformatics, Data Mining, Deep Learning
	\item[] third year: Theory of Computation
	\item[] second year: Object Oriented Programming
\end{itemize}


\end{description}
\end{description}
\label{f0}
% html: End of file: `experience.html'
