% html: Beginning of file: `admin.html'
\begin{description}\item[] \begin{description}\item[] {\large \bf Administration Responsibilities  }
\begin{description}
\item[ {\bf 1987-2002:}]
\item[ {\bf Lab responsibilities} ]  Before we had a technical team 
                               I was responsible for
                               running UNIX servers within
                               Computer Science.  These have ranged from
                               an HP 9000 with 3 workstations under HPUX
                               to 2 SGI Indys under Irix and
                               an 8 machine Linux network.
\item[ {\bf  Faculty web site } ]  For about six years I was
     responsible for Computer Science and Faculty web sites. 
\item[ {\bf 2003-2004:}]
\item[ {\bf  Head of Department} ]
     During this period I have acted as Deputy Head of
     School, Head of Discipline, Programme Director 
     and acting Head of Department in the absence of
     Prof Sartori-Angus. 
     I was involved with a number of
     academic appointments, the fulltime appointment of our first
     technical manager and the re-grading of administation staff. \newline
     During 2003 we were forced into a merger with Geology. 
     I played a large part in the operation of our School
     of Geological and Computing Sciences.
     I pursued geocomputing projects
     two of which have resulted in MSc theses under my supervision.
     My image processing and mathematical modelling experience
     were found useful to the geologists and I have acted as entertainment officer, 
     seminar series organizer and coffee maker. \newline
     During 2004, I accepted a professorship on the Pietermaritzburg campus
     where  I acted as head of discipline for Computer Science.
     I also played a large part in the
     planning process for a split from Geology and the formation of a 
     new School of Computer Science that was
     due to get underway at the beginning of 2005.\newline
\item[ {\bf 2005-2011:}]
\item[ {\bf  Head of School} ]     
     At the beginning of 2005 I accepted a three year
     contract as {\it Head of School}
     for the new UKZN School of Computer Science which operated across  
     Pietermaritzburg and Durban. The new School consisted of 19 academics,
     4 administrators and 6 technical staff.\newline
     I took sabbatical in 2008 and returned in 2009 as 
     deputy head of School.
     During 2011 I took on the responsibility of one
     more year as Head of School before our School was again
     merged, this time with Mathematics and Statistics.
     During 2012 I took sabbatical and have returned to a
     teaching position for 2013 and 2014.
     

\end{description}
\end{description}
\end{description}
\label{f0}
% html: End of file: `admin.html'
