% html: Beginning of file: `teaching.html'
\begin{description}\item[] \begin{description}\item[] {\large \bf Course Development:} 
 I have been responsible for the development
 of a number of courses during my tenure at UND and UKZN.\newline
\item[Java Programming.] I played a large part in the move to JAVA based programming 
and have regularly taught the first year introductory JAVA programming course.
 \item[Discrete Mathematics,]  I was responsible for a large part of the development of our first year
      course introducing number representation and logic to Computer Science students. 
 \item[Data Structures,]  I offer a standard second year Data Structures course which can be delivered
      using either JAVA or C++.
 \item [Numerical Analysis,] I developed most of the content for this second year
       course which has since been taken over by Mathematics.
 \item[Graphics and Modeling,]  I developed this web based third year course using the 
          medium of {\tt VRML} to impart graphics concepts. 
 \item[Operating Systems,]
      I have been entirely responsible for the development of this course
      which is now a common course across all 
      delivery sites of Computer Science.
      This course is popular with students as it is the first time they
      get experience with Linux and multi-player computer games.
 \item[Mathematical Modeling,]  This honours course,  is based on the
      package, {\em  Mathematica}.
      I am responsible for the entire content of this
      course and have since become
      the University's resident {\em Mathematica} expert.
 \item[Image Processing]  This honours course is delivered using
      the Java based image processing shell, ImageJ. 
 \item[Bioinformatics,]  After obtaining the NBN grant, I developed a 
      Bioinformatics honours course pitched at Computer Science students 
      who have an interest in genetics. 
      A number of these students have since completed masters in
      bioinformatics after an introduction via this honours course.
 \item[Data Mining,] During my 2012 sabbatical I developed a new honours 
      course introducing data mining and machine learning in an R programming
      environment. 
  \item[Deep Learning,] In the second semester of 2018,  for the first time at UKZN, 
  I taught  a {\it deep learning} honours module to Mathematics students. The inspiration
  for this module came from a 2015 online set of lectures by Nando de Freitas of Oxford university.
  The course notes have been written up and published online as a free to download textbook.
  The notes are accompanied by a set of {\tt Jupyter notebooks} that implement the networks described in the
  text using the {\tt Julia} programming language together with the {\tt Flux} deep learning package.
  The notes and the notebooks are available from \url{https://hughmurrell.github.io/DeepLearningNotes}.
   
\end{description}

\end{description}
\label{f0}
% html: End of file: `teaching.html'
