% html: Beginning of file: `postgrads.html'
\begin{description}
\item[Postgraduate supervision]
\begin{description}
\item[]
\item[Hilton Goldstein,] MSc thesis, 1990, \\
      {\em Computer Enhanced Skull Surgery}, \\
      a graphics system that used CAT data to
          help surgeons make decisions on which piece of skull to use when
          reconstructing a forehead for children suffering from dwarf syndromes.
\item[Hilton Goldstein,] PhD thesis, 1994, \\
      {\em Space Frequency decomposition of arbitrary signals}, \\
        Space/Frequency decomposition of one dimensional
          signals. using wavelets to construct a {\em  dominant scale algorithm }
          for which applications in music and speech recognition exist. This
          PhD resulted in two journal papers
          and two conference presentations.
\item[Cuan Brown,] MSc thesis, {\em cum laude}, 2000,\\
      {\em A Real Time, Secure, Internet Based, Auctioning System},\\
          A web based auctioneering system.
          Bidding was controlled by java applets running under client web browsers
          and communicating with a java controller on the host auction server.
          The latest cryptographic techniques were employed to protect the bidders
          and the auctioneer.
\item[Mark Lewis,] MSc thesis, 2001, \\
      {\em Spectral Techniques for Roughness Estimation},\\
          Spectral based algorithms
          for estimating the {\em  roughness } of 1D and 2D signals. Applications
          in geology and biology were tackled. This project
          has produced one paper in SACJ.
\item[Theo Naicker,]  MSc thesis, 2002, \\
      {\em Modelling the two body abrasive wear problem},\\
          A computer model for the two-body
          abrasive wear problem in response to a request from the DeBeer's mining company.
          This problem involves the study of how one surface, the tool surface,
          will degrade another surface, the work surface,
          when they come into contact while in relative motion.
\item[Keagan Moodley,] MSc thesis, {\em cum laude}, 2002, \\
      {\em Pseudo-Colouring of grayscale images},\\
      an extension of his pseudo colouring honours project
          to allow for colour maps to be generated from many different colour models
          with applications
          such as, sonar images of sea beds and x-ray medical scans.
          This project produced a paper in SACJ.
\item[Luke Vorster,] MSc thesis, 2004, \\
       {\em A UML framework for computer music}, \\
       A general framework for computer
          music based on UML (the Unified Modelling Language).
 
 \newpage        
\item[Kieran O'Neill,] MSc thesis, {\em cum laude}, 2007, \\
       {\it Relieving the Cognitive Load of Constructing Molecular
       Biological Ontology Based Queries by means of Visual Aids}, \\
       Co-Supervisors: Daniel Jacobson and Alexander Garcia-Castro.
\item[Rafael Jimenez,] MSc thesis, 2007, \\
       {\em Vector Graphics to improve Blast Graphic
       Representations}, \\
       Co-Supervisors: Daniel Jacobson and Alexander Garcia-Castro.
\item[John McGuiness,] MSc thesis, {\em cum laude}, 2009, \\
       {\em Investigation of techniques for automatic polyphonic
       music transcription using wavelets,} \\
       a bold attempt to produce software that constructs musical
       scores from sound recordings.
\item[Anisa Ragalo,] MSc thesis, {\em cum laude}, 2011, \\
        {\em An analysis of algorithms to estimate the characteristics 
        of the underlying population in Massively Parallel Pyrosequencing data,}
        A Mathematica platform for evaluating various Pyrosequencing algorithms.
\item[Devin Pelser,] Msc thesis, 2019, \\
        {\em Deep and dense sarcasm detection, } A deep, dense neural network for detecting sarcasm.
\end{description}
\end{description}
\newpage
\label{f0}
% html: End of file: `postgrads.html'
