% html: Beginning of file: `publications.html'
\begin{description}\item[] \begin{description}\item[] {\bf  Publications  }
\begin{description}
\item[1982:]
      {\it From Cagniard's Method to the method of the Differential Transform},
      Comp. \& Maths. with Appls., Vol. 8, No. 2, pp.103-118, Co-Author:
      Abraham Ungar.\newline
\item[1985:]
      {\it The Differential Transform and its application to an electrostatics
      Image Problem}, Comp. \& Maths. with Appls., Vol. 11, No. 6,
      pp.565-572, Co-Author: Abraham Ungar.\newline
\item[1986:]
      {\it Non-Linear runoff routing, a comparison of solution methods},
      Journal of Hydrology, 85, pp.339-347, Co-Author: Dennis Hughes.\newline
\item[1989:]
      {\it A case for Computer Tomography in the Undergraduate
      Syllabus}, proceedings of the 15th South African symposium on
      Numerical Mathematics, Umhlanga Rocks, July 1989.\newline
\item[1990:]
      {\it Image Reconstruction via the Hartley transform}, South
      African Computer Journal, Number 1, pp36-42, Co-Author:
      David Carson.\newline
\item[1991:]
      {\it A model of age-dependent population dynamics providing simple criteria
      for growth or extinction}, Mathematical Biosciences, 103, pp1-17,
      Co-Author: John Swart.\newline
\item[1992:]
      {\it Animation of rotating rigid bodies}, The Mathematica Journal,
      Vol. 2, No. 1, pp.61-65.\newline
\item[1993:]
      {\it A mathematical golf swing}, The Mathematica Journal,
      Vol. 3, No. 4, pp.62-65. \newline
\item[1994:]
       {\it Planar Phase Plots and Bifurcation Animations},
       The Mathematica Journal, Vol 4, No. 3, pp.80-85 \newline
\item[1995:]
       {\it Wavelets and Birdcall Recognition},
       Proceedings of the 25th annual SACLA conference,
       pp.51-62, (copies from Rhodes University).\newline
\item[1996:]
      {\it Computer Aided Tomography},
      The Mathematica Journal, Vol 6, No. 2, pp.60-65 \newline
\item[2001:]
      {\it On Measuring Roughness}, South African Computer Journal,
      Number 27, pp 49-56, Co-Authors:
      Mark Lewis, Colin Jermy and Tally Palmer. \newline
 \item[2004:]
      {\it A colour-map plugin for the open source, Java based,
      image processing package, ImageJ},
      Computers \& Geosciences, vol 30, pp 609-618.
      Co-Author: Keagan Moodley. \newline
\item[2007:]
      {\it An oscillatory model revisited},
      Chaos Solitons and Fractals, Vol 32, issue 4, pp 1325-1327.
      Co-Author: John Swart. \newline
\item[2008:]
      {\it A generalised Verhulst model of a population
      subject to seasonal change in both carrying capacity
      and growth rate},
      Chaos Solitons and Fractals, Vol 38, issue 2, pp 516-520.
      Co-Author: John Swart. \newline
\item[2008:]
      {\it Gene Spotting with Support Vector Machines},
      Proceedings of IMS2008,
      Maastricht. \newline
\item[2009:]
      {\it Classification of the maxillary sinus
      according to area of the medial antral wall:
      a comparison of two ethnic groups},
      J Maxillofac Oral Surg, Vol 8, issue 2, pp 103–107
      Co-Authors: CL Fernandes and CMC Fernandes. \newline
\item[2011:]
      {\it Fisher Discrimination with Kernels},
      The Mathematica Journal, Vol 13, July 26,
      Co-Authors: Kazuo Hashimoto and Daichi Takatori. \newline
\item[2012:]
       {\it Matie, Measuring Association and Testing Independence Efficiently},
       a presentation at {\it The Data-mining Revolution}, a bioinformatics conference in Stellenbosch. 
       % See \url{abstracts.genetics.cmc-uct.co.za/presentations/OP52.pdf} for details. 
       Co-Authors: Ben Murrell and Daniel Murrell.\newline
\item[2013:]
       {\it Synchronisation of fertility with carrying capacity; 
       an investigation using classical and agent based modeling},
       South African Computer Journal, Number 50,
       Co-Author: John Swart. \newline
\item[2014:]
         {\it $R^2$-equitability is satisfiable}, Proc Natl Acad Sci USA , early edition, 
         Co-Authors: Ben Murrell and Daniel Murrell. \newline
% \item[2014:]
%	{\it Discovering general multidimensional associations},
%	in preparation for publication with a preview available at 
%	\url{http://arxiv.org/abs/1303.1828},
%	Co-Authors: Ben Murrell and Daniel Murrell.
\item[2016:]
         {\it Discovering General Multidimensional Associations},
         PLoS ONE 11(3): e0151551. doi:10.1371/journal.pone.0151551
	Co-Authors: Ben Murrell , Daniel Murrell. \newline
\item[2019:]
         {\it Deep and dense sarcasm detection},
         \url{https://arxiv.org/abs/1911.07474}, November 2019,
         Co-Author: Devin Pelser. \newline
 \item[2019:]
 	{\it Deep Learning Notes, with Julia and Flux}, Edition 1,
	\url{https://HughMurrell.github.io/DeepLearningNotes}
	Co-Author: Nando de Freitas.

\end{description}
\end{description}
\end{description}
\label{f0}
% html: End of file: `publications.html'
